Realistically Interesting Domains for Probabilistic Planners

### 2014-04-10 FinalPaper/paper.tex
changed structure of the paper

\section{Future Experiment}
\label{sec:experiment}

Experiments can empirically evaluate the performance of the adjusted domains.

\subsection{Setup}

The planning problems are taken from the IPPC-11 suite and are written in RDDL,
which are publicity available. A domain consists of the domain description and
instances of a domain problem. The domain description is read by RDDLSim, which
is a server a planner can communicate with, and simulates the real world after
the planner sends an action.

\subsection{FF-Replan with Finite Horizon}

\textsc{Gourmand} already works with RDDLSim and MDPs with finite horizon. The original
FF-Replan is a Goal-Oriented MDP planner. For a Finite-Horizon each state at
the horizon is a goal. To compare \textsc{Gourmand}, that works with MDP-FH, with
FF-Replan, FF-Replan needs a slight update. It should not only execute FF for
one goal, but for all goals at the horizon. It could then start executing the
plan with the highest reward. Depending on the determinization method,
\emph{single-outcomes} or \emph{all-outcomes}, not all goals might be
reachable. Of course the performance decreases with an increase of goal states
at the horizon. A hash-table cache, as FF-Replan already uses can still be used
to store plans generated by FF from a state to goal states, however not only
the plan should be stored, but also the reward for this plan should be stored
to pick the plan with the highest expected reward.

Using the framework of \textsc{Glutton} and \textsc{Gourmand}, and the FF heuristic found in mGPT
\cite{bonet2011mgpt}, the updated FF-Replan can be implemented. The first step
of \textsc{Gourmand} is parsing the problem and creating a structure of the problem.
Instead of executing the \textsc{Gourmand} algorithm, this structure can be used to
determinize the problem by setting all probabilities of each action to 1
(\emph{all-outcome}) or all but one to 0 (\emph{single-outcome}). Using the
FF heuristic it can find plans for each goal and calculate the expected reward.
Then it can reuse the \textsc{Gourmand} framework to execute the plan by sending the
action to the RDDLSim server. Like FF-Replan if the server returns with a state
that is not in the plan the algorithm will replan. If a goal is reached it will
output the achieved reward.

\subsection{Hypothesis}

@@

In sections above we have described the GOURMAND planner and FF-Replan as two
probabilistic planners of the IPPC competition.
RFF~\cite{teichteil2010incremental} is an offline planner that generates a
policy: for each reachable state it determines a plan to the goal. Like
FF-Replan it uses determinization and FF\. FF returns an initial plan from the
initial state to a goal state. For each state in the plan the successor states
are added to the structure, after which Monte-Carlo sampling is used. States
where the probability that they're reached is too low (below a threshold) are
removed. The successor states are used as initial states in the next step. If
FF fails to find a plan to the goal from this new state, the state is removed
from the structure too. Results showed that RFF outperformed other competitors.
A higher threshold means that RFF will generate more policies that are prone to
replanning.

\subsubsection{PROST ?}

\subsection{Probabilistic planning vs Replanning}
Inspired by the FF-Replan entrance in the IPPC competition, this paper described a probabilistic interestingness quality of domains. It then compares probabilistic planners with replanners in the different domains to draw conclusions. Classical planning with replanning upon failure when there is so little or so much uncertainty about the world that it is not worth modelling and reasoning about or when goals dynamically change or when the problem is too large to solve at once. Probabilistic planners are more appropriate when avoiding irreparable or costly failures. Probabilistic planning computes a plan that can handle all foreseeable contingencies and is preferable for quick reactions in closed control loops.

The following structural properties are identified for comparing probabilistic planning with replanning:
\begin{itemize}
	\item `dead' end states
	\item the degree to which the probability of reaching a dead end state can be reduced through choice of actions
	\item number of distinct trajectories
	\item presence of mutual exclusion
\end{itemize}

If there are no dead ends, a replanner will always succeed. It is impossible to improve on the unavoidable dead ends (positive probability of reaching when executing which cannot be reduced without reducing the probability of reaching the goal).

% repetition of what's already stated earlier

A probabilistic planning problem is considered to be probabilistically interesting if and only if it has all the following structural properties:

Problems that fail to be \emph{probabilistically interesting} are actually classical planning problems in disguise and for those replanners are more appropriate. A replanner can also perform optimally for probabilistically interesting planning problems whenever the `most promising' goal trajectory is the correct thing to do. They create several domains to explore the issue of replanning vs\@. probabilistic planning.

Following existing domains were said to be probabilistically interesting:
\begin{itemize}
	\item Drive
	\item Exploding blocksworld
	\item Pitchcatch
	\item Schedule
	\item Tireworld
\end{itemize}

They conclude by stating that the negative perception of probabilistic planning by the ICAPS community was inaccurate. They state that a synthesis of planning and replanning techniques could make a larger number of probabilistic planning problems practicably solvable than is currently possible.

@@

>>>>

%-------------------------------------------------------------------------------------------------------------------------------------

@@

%In sections above we have described the GOURMAND planner and FF-Replan as two
%probabilistic planners of the IPPC competition.
%RFF~\cite{teichteil2010incremental} is an offline planner that generates a
%policy: for each reachable state it determines a plan to the goal. Like
%FF-Replan it uses determinization and FF\. FF returns an initial plan from the
%initial state to a goal state. For each state in the plan the successor states
%are added to the structure, after which Monte-Carlo sampling is used. States
%where the probability that they're reached is too low (below a threshold) are
%removed. The successor states are used as initial states in the next step. If
%FF fails to find a plan to the goal from this new state, the state is removed
%from the structure too. Results showed that RFF outperformed other competitors.
%A higher threshold means that RFF will generate more policies that are prone to
%replanning.

\subsubsection{PROST ?}
\todo{wrote sentence about Prost - Arian}\\

\todo{rewrite prob int - Imara}

%\subsection{Probabilistic planning vs Replanning}
%Inspired by the FF-Replan entrance in the IPPC competition, this paper described a probabilistic interestingness quality of domains. It then compares probabilistic planners with replanners in the different domains to draw conclusions. Classical planning with replanning upon failure when there is so little or so much uncertainty about the world that it is not worth modelling and reasoning about or when goals dynamically change or when the problem is too large to solve at once. Probabilistic planners are more appropriate when avoiding irreparable or costly failures. Probabilistic planning computes a plan that can handle all foreseeable contingencies and is preferable for quick reactions in closed control loops.
%
%The following structural properties are identified for comparing probabilistic planning with replanning:
%\begin{itemize}
%	\item `dead' end states
%	\item the degree to which the probability of reaching a dead end state can be reduced through choice of actions
%	\item number of distinct trajectories
%	\item presence of mutual exclusion
%\end{itemize}
%
%If there are no dead ends, a replanner will always succeed. It is impossible to improve on the unavoidable dead ends (positive probability of reaching when executing which cannot be reduced without reducing the probability of reaching the goal).
%
%% repetition of what's already stated earlier
%
%A probabilistic planning problem is considered to be probabilistically interesting if and only if it has all the following structural properties:
%
%\begin{itemize}
%	\item there are multiple goal trajectories;
%	\item there is at least on pair of distinct goal trajectories, $\tau$ and $\tau$ ', that share a common sequence of outcomes for the first n-1 outcomes, and where $\tau$\textsubscript{n} and $\tau$'\textsubscript{n} are distinct outcomes of the same action; and
%	\item there exist two distinct goal trajectories $\tau$ and $\tau$' and outcome o $\in$ $\tau$ and o' $\in$ $\tau$' of two distinct actions a = act(o) and a'= act(o') such that executing a strictly decreases the maximum probability of reaching a state where a' can be executed.
%\end{itemize}
%
%Problems that fail to be \emph{probabilistically interesting} are actually classical planning problems in disguise and for those replanners are more appropriate. A replanner can also perform optimally for probabilistically interesting planning problems whenever the `most promising' goal trajectory is the correct thing to do. They create several domains to explore the issue of replanning vs\@. probabilistic planning.
%
%Following existing domains were said to be probabilistically interesting:
%\begin{itemize}
%	\item Drive
%	\item Exploding blocksworld
%	\item Pitchcatch
%	\item Schedule
%	\item Tireworld
%\end{itemize}
%
%They conclude by stating that the negative perception of probabilistic planning by the ICAPS community was inaccurate. They state that a synthesis of planning and replanning techniques could make a larger number of probabilistic planning problems practicably solvable than is currently possible.

@@

\section{Future works}
